The \dealii Library, Version 9.5

### 2023-06-26 9.5/paper.tex

>>>>

\subsubsection{Uniform interface for nonlinear solvers}\label{sec:nonlinear}

With the current release, \dealii{} now supports solvers for nonlinear problems
provided by several different external packages:
(i) KINSOL (part of SUNDIALS); (ii) SNES (part of PETSc, see Section~\ref{sec:petsc}); and (iii) NOX (part of Trilinos, see Section~\ref{sec:trilinos}).
The wrappers are provided by the classes \texttt{PETScWrappers::NonlinearSolver<VectorType>}, \texttt{SUNDIALS::KINSOL<VectorType>}, and \texttt{TrilinosWrappers::NOXSolver<VectorType>}, respectively.

All three of these classes have a very similar interface, except that they vary in the kind of
algorithms and parameters offered. The new class \texttt{NonlinearSolverSelector<VectorType>} provides a wrapper on top of
the three external solvers with a unified interface. The user can either let
\dealii{} decide which of the packages to use (depending on the current availability of
the external packages) or specify it manually.

Here is a complete example of an MPI parallel Newton solver that automatically chooses one of the available packages:
\begin{c++}
    using NLSolver = NonlinearSolverSelector<LA::MPI::Vector>;

    NLSolver::AdditionalData additional_data(NLSolver::automatic,
                                             NLSolver::newton);
    NLSolver nonlinear_solver(additional_data, mpi_communicator);

    nonlinear_solver.reinit_vector = [&](LA::MPI::Vector &x)
                                     {/*...*/};
    nonlinear_solver.residual = [&](const LA::MPI::Vector &evaluation_point,
                                    LA::MPI::Vector &      residual)
                                {/*...*/};
    nonlinear_solver.setup_jacobian = [&](const LA::MPI::Vector &current_u)
                                      {/*...*/};
    nonlinear_solver.solve_with_jacobian = [&](const LA::MPI::Vector &rhs,
                                               LA::MPI::Vector &      dst,
                                               const double tolerance)
                                           {/*...*/};

    nonlinear_solver.solve(current_solution);
\end{c++}
